### 2002-09-23 dialoguesisters/en/DialogueSisters.tex
no message

When Martin leaves the bus, he has almost reached his destination. 

@@

twilight spreads in the narrow valley between the ridges of the 

@@

and Martin feels pretty quickly abandoned.
He already misses the silent company of the people on the bus. 

@@

is the house in which he 
will be carrying out alternative service as a {\em Zivi\/}\footnote {{\em
    Zivi} = abbr.\ of `Zivildienstleistender' (literally someone performing civil services in Germany).

@@

In the first days Martin is occupied to find the way about in his new surroundings. 
Not only must he introduce himself to superiors, doctors and to the nursing staff and
familiarise himself with the customs in the extensive building, but he has to adjust

@@

This is not an easy thing for a twenty-year-old who has spent most part of his 
previous life sheltered at school.

@@

Although the clinic on the one hand is furnished very modern and although every only

@@

Martin keeps away from his colleagues and limits contacts to the day-to-day 
operations and some friendly words during meals. 

@@

nursing administration. 

@@

Doris\/}, he begins to confide his impressions to his laptop's electronic diary. 

@@

When I entered with Dr.~Weissenborn Anna's room, she got up immediately from her 

@@

-- This comes from the Bible which lay opened before Anna on the table (after her 

@@

She is 22~years old, autistic and comes from an orthodox Roman Catholic parents` home. 

@@

She took no other notice of me, anyhow, I have read no reaction from her features, as Dr.~Weisenborn has pointed me out to her. 

@@

The 17-year-old had hardly seen me, he jumped at me, was faced up to me with all of 
his one metre ninety and roared: `Do you play chess?' 
Besides, he didn't even look at me! 

@@

`I know at least the rules.' `Then let us play!' 

@@

`Later, Rudolf, later' calmed him Dr.~Weissenborn. `Martin must work now.'
`However, he has promised to play with me!' Yes, Rudolf, but not now. Perhaps 
tonight. `However, \dots' 
With some effort we tore ourselves away. 

@@

He can't read a single letter, and if he screams at you, do not take offence at him. 

@@

And, by the way, Rudolf has reminded me of something which you absolutely must 

@@

I would like to introduce to you Martin. He will also be living with us here for a while. 

@@

Both are older than thirty and have been living for a long time in this clinic. 

@@

But a longer talk with Bianca and Doris is impossible! 
Suddenly the sisters proceed their dialogue using number hieroglyphs, and Martin is 

@@

but in fact a secret language.

@@

that no one can follow their dialogue, and this gives them absolute privacy. 

@@

else, especially because no one beyond the gates of the clinic would be listening. 
Because Martin likes the sisters, this causes some little pain to him. 

@@

Martin could once unintentionally listen to a discussion between two hospital physicians 

@@

Even though he loses each game and causes Rudolf several times to be happy, he 
sharpens thereby his analytic skills and improves appreciably his strategy. 

@@

Martin rapidly closes the drawer and puts the card from the bath in his trouser 

@@

He leaves her behind and follows his thoughts farther: `These deleted pair of 

@@

Thereby the first problem already begins that the sisters utter their numbers very 

@@

administration during his lunch time. 

@@

Lacking any better inspiration, Martin proceeds from the obvious basic assumption 

@@

Martin is frustrated: there are as many as desired possibilities for such a coding. 

@@

Fine so. Now to the code. 

@@

Martin hasn't got the slightest idea.

@@

Martin speaks again loudly with himself. 

@@

\begin{center} 
{\bf V.} 
\end{center} 
In the course of the next days Martin feels bad-tempered and tired at his work. 
The initial euphoria about the discovery of the encoding mechanism has given way to a sheer frustration. 
Certainly, he has written a program with his laptop with which he can encode all letters after input of a 
pair of code numbers, but the decoding gives him a hell of a puzzle. 
Even with the knowledge of a key he has no plan of how he can win the corresponding number between 1 and 26 
from the number which represents a letter. The numbers between 1 and 26 then identify the letter in the alphabet.
Up to now he controls only the mechanism of {\em encoding\/}, but not the one of {\em decoding\/}; and for 
communication with Bianca and Doris just the decoding is particularly important. 
Only in the case if the coding exponent is set to 1, the letters keep their alphabetically given numbering from 
1 to 26, and then a simple division with a remainder reduces the numbers to the letters. 
But the sisters never use the encoding exponent~1. \dots -- \\ 
Martin also has his own feelings about the bizarre world of Bianca and Doris. 
He puts them into his electronic diary: \\ \\ 
`Who knows according to which plan Bianca and Doris transform their words into numbers and decipher them again?
Even if this mechanism can be described by formulae and should run in a usual programming language in the 
computer, it doesn't mean that Bianca and Doris adhere to the same principles. 
Already the rate, with which they get along thereby without technical aids, is a note on the fact that in their
brains probably something runs {\em completely differently \/} to other people. 
How can it otherwise be understood that {\em Mozart \/}, who has heard coincidentally a mass somewhere, could 
write it down later from memory without an error and completely in score? 
Most of all {\em Mozart \/} and {\em Einstein \/} were humans, who had only the luck that they found highest 
social acknowledgment with the results of their unusual networking in the brain. 
Between Rudolf's astute chess strategies and the ability of Mozart to be able to compose a whole opera only 
in his head no gradual difference exists. 
Only the objects are others and the attitude of `normal' humans to them!! 
If Anna says the whole psalter by heart, she belongs in this sense to the degree migraters between genius and 
madness, even if nobody wants to hear her monologues. -- \\ 
In this sanatorium something is rather lugubrious: I can {\em sense\/} it, and Bianca and Doris {\em know\/} 
what it is! 
Perhaps I will finally get to the bottom of it. 
How on earth can Dr.~Weissenborn consider the sisters to be  insane? 
In a surroundings felt hostile by them their encoded communication provides to them a feeling of security. 
Is it different with us so-called `normal' beings in the world outside?
Who is not afraid with homebanking or with cash dispensers that strangers can get into the secrets? 
Nevertheless, nowadays a modern person can no longer manage without secret numbers! 
Madness is a pure definition thing!!'

@@

In spite of intense reflection Martin fails to solve the problem of decoding Bianca's and Doris' secret language. 
Nevertheless he does not give up: He uses a free day, goes to Heidelberg and meets there with {\em Dr.~Praetorius\/} 
in the Maths Department of the university. 
Martin had got in touch with this man whose name he had found trace in the personal catalogue of the university, 

@@

The academic receives him friendly and listens patiently, when Martin tells to him of his work, the sisters and 

@@

Then Martin explains to him the encoding technique, as far as he could already analyze it.

@@

the Zivi does not mention. \\ \\ 

@@

Martin hands him the playing card which he had found behind the mirror in the sisters' bathroom, and the academic 

@@

`Nevertheless, you know what prime numbers are?' 

@@

The result, besides, we want to name {\em auxiliary module\/}.' 

@@

`Can you indicate me a number which has the following property: 

@@

`Well, one must hit upon this first!', means Martin, `no miracle that I have not cracked this problem!' 

@@

The young man gives the academic an unbelieving look. 

@@

But now he is of full confidence to be able to communicate with Bianca and Doris in the future without limits. 
Nevertheless, now with the help of the dictaphone, the laptop and his knowledge this should be possible! 

@@

\begin{center} 
{\bf VII.} 
\end{center} 
Although Martin returns late in the evening to the sanatorium, he still sits down to his laptop and 
maps out a decoding program. 
Already on the bus ride he had made some sketches, describing the decoding concept of Dr.~Praetorius. 
He checks it with the key {\bf 51\,,\,3} for the coding of the sentence I AM BIANCA. 
It runs perfectly. 
Now together with the coding program he already had finished some days ago, Martin disposes of a complete 
interpreter's system for the secret language of the sisters. 
Dr.~Praetorius had forecast correctly that the associated programs are not complicated at all and the 
routines run very quickly. 
One can master separate words or short sentences also with a pocket calculator, but not longer conversations.
Here only the laptop can help. 
Finally, overtired, but altogether satisfied with himself, Martin falls into the bed. \\ \\ 
Martin's first task in the morning is to look after `his charges'. 
Rudolf and Anna are late risers, but Bianca and Doris get up very early in the morning. 
With palpitation Martin enters into their room; he has brought the dictaphone and the laptop with him. 
The sisters sit silently at their living room table, they do not react to Martins friendly `Good morning'. 
They also remain quiet, when he puts both devices on the table.
`This behavior must indicate something!' the Zivi asks himself. `Of course!' it suddenly comes to him. 
`The password of the day! At the bathroom mirror!' 
And correctly, the sisters have hidden deliberately a playing card behind the mirror for Martin. 
They must have suspected that he will communicate today in their way with them. 
The password of the day reads: 
\begin{center} 
{\bf 681\,,\,151\,\,.}
\end{center} 
Martin turns to the women at the desk. 
He puts in the code key and translates the words GOOD MORNING. 
He reads out the numbers on his display loudly. 
The spell is broken. 
The sisters answer encoded, Martin translates back. 
At first he still uses the dictaphone, but, finally, he notices that it works fine without recording equipment. 
Soon he has the exercise and types the numbers of the women directly during their conversation; his laptop 
translates in lightning speed. 
Certainly, it is a little bit slower than the sisters are accustomed to between themselves because Martin must 
serve the keyboard. 
But the conversation is fluent, even if rather unusual. \\ 
Gradually Martin passes over from the talk of the insignificance to the doctors and nurses in the house. 
Finally: He types the question with shaky hands in his computer WHAT DO THEY DO WITH YOU IN THE TOWER.
While he is reading out the numbers of the encoding, he receives a dry neck. 
It is Doris who answers: 
\begin{center} 
4258, 7182, 9168, 6089, 1734, 9391, 8487, 1363, 853, 10898, 12618, 10512, 172, 7493, 1734, 10229, 7182, 13105 \,\,. 
\end{center} 
`A short answer', thinks Martin, before he operates the key for the execution of the translation. 
It takes less than a second for the machine to work. 
Martin stares aghastly at the screen of his laptop. 
He cannot believe what he is reading. 
But then he acts rapidly. -- \\ \\ 
A few days later a huge scandal is uncovered in the Odenwald clinic and is condemned throughout the nation.

@@

\noindent
{\em Note of the author:\/}
\begin{itemize}
\item[(1)] In order not to confuse the reader, a necessary mathematic
  presupposition was not mentioned with the description of the coding
  procedure.  However it is not required for the purposes of this story.
  Nevertheless, it should be mentioned here on behalf of the completeness
  that not {\em every\/} arbitrary pair of numbers is suitable as a coding
  code where the main module is a product of two prime numbers.  Rather
  should be respected the fact that the auxiliary module and the encoding
  exponent have {\em no common devisor\/}.
  Otherwise one would find no decoding exponent. \\*[+2pt]
  {\bf Example}: The pair 35\,,\,15 is not good as a coding code
  because the auxiliary module \((5-1) \cdot (7-1) =24\) and the coding
  exponent \(15\) have the common divisor \(3\).
\item[(2)] However, in practical applications one does not encode a text literally
as it is described in the story as a so-called RSA-procedure.  One
block-likely codes a text, while one combines the letters of the text
sequentially to blocks of firm length and assigns with a certain procedure
to these blocks {\em a separate number\/}.

\item[(3)] Besides it is usual in the practice -- in contrast to Doris' and
Bianca's method of approach -- to present the coding not in a form of
numerical orders, but in letters which prove naturally no sense as a text.

>>>>

When Martin gets off the bus, he has almost reached his destination. 

@@

twilight spreads in the narrow valley in between the ridges of the 

@@

and Martin feels pretty quickly abandoned. He already misses the silent company of the people on the bus. 

@@

is the house in which he will be carrying out alternative service as a {\em Zivi\/}\footnote {{\em Zivi} 
= abbr.\ of `Zivildienstleistender' (literally someone performing civil services in Germany).

@@

In the first days Martin is busy finding his way about in his new surroundings. 
Not only does he have to introduce himself to superiors, doctors and the nursing staff as well as 
familiarising himself with the customs in the extensive building, but he has to adjust

@@

This is not an easy thing for a twenty-year-old who has spent the main part of his 
previously sheltered life at school.

@@

Although the clinic on the one hand has very modern furnishings and although every only

@@

Martin keeps away from his colleagues and limits contact to the day-to-day 
operations and some polite words during meals. 

@@

nursing staff. 

@@

Doris\/}, he begins to confide his impressions to electronic diary on his laptop. 

@@

When I entered Anna's room with Dr.~Weissenborn, she got up immediately from her 

@@

-- This comes from the Bible which lay open in front of Anna on the table (after her 

@@

She is 22~years old, autistic and comes from a home with an orthodox Roman Catholic parents. 

@@

She takes no other notice of me, anyhow, I read no reaction from her features, as Dr.~Weissenborn has pointed me out to her. 

@@

The 17-year-old had hardly seen me, he jumped at me, faced up to me with all of 
his height of one metre ninety and roared: `Do you play chess?' moreover, he didn't even look at me! 

@@

`Well, I mean, at least I know the rules.' `Then let us play!' 

@@

`Later, Rudolf, later' said Dr.~Weissenborn reassuringly. `Martin has got to work now.'
`However, he has promised to play with me!' Yes, Rudolf, but not now. 
Maybe tonight. `However, \dots' With some effort we tore ourselves away. 

@@

He can't read a single letter, and if he screams at you, do not take offence. 

@@

And, by the way, Rudolf has reminded me of something which you need to 

@@

I would like to introduce you to Martin. He will also be living with us here for a while. 

@@

Both are older than thirty and have been living for a long time the clinic. 

@@

But any longer discussion with Bianca and Doris is impossible! 
Suddenly the sisters continue their dialogue using number hieroglyphs, and Martin is 

@@

but there is in fact a secret language.

@@

that no one can follow their dialogue, and this gives them total privacy. 

@@

else, especially because no one beyond the gates of the clinic would listen. 
Because Martin likes the sisters, this fact hurts to him. 

@@

Martin once accidentally overheard to a discussion between two hospital physicians 

@@

Even though he loses every game and causes Rudolf several times to be happy, he 
then sharpens his analytic skills and improves appreciably his strategy. 

@@

Martin quckly closes the drawer and puts the card from the bath in his trouser 

@@

He leaves her behind and is once again buried deep in thought: `These deleted pair of 

@@

Thereby the first problem is already that the sisters utter their numbers very 

@@

administration during his lunch break. 

@@

Lacking any better inspiration, Martin starts with the obvious basic assumption 

@@

Martin is frustrated: there are an infinite number of possibilities for such a coding. 

@@

So far, so good. Now to the code. 

@@

Martin hasn't got the faintest idea.

@@

Martin talks again loudly to himself. 

@@

\begin{center} 
{\bf V.} 
\end{center} 
In the course of the next days Martin feels bad-tempered and tired at work. 
The initial euphoria about the discovery of the encoding mechanism has given way to a sheer frustration. 
Certainly, he has written a program with his laptop with which he can encode all letters after input of a 
pair of code numbers, but the decoding gives him a hell of a puzzle. 
Even with the knowledge of a key he has no plan of how he can win the corresponding number between 1 and 26 
from the number which represents a letter. The numbers between 1 and 26 then identify the letter in the alphabet.
Up to now he controls only the mechanism of {\em encoding\/}, but not the one of {\em decoding\/}; and for 
communication with Bianca and Doris just the decoding is particularly important. 
Only in the case if the coding exponent is set to 1, the letters keep their alphabetically given numbering from 
1 to 26, and then a simple division with a remainder reduces the numbers to the letters. 
But the sisters never use the encoding exponent~1. \dots -- \\ 
Martin also has his own feelings about the bizarre world of Bianca and Doris. 
He puts them into his electronic diary: \\ \\ 
`Who knows according to which plan Bianca and Doris transform their words into numbers and decipher them again?
Even if this mechanism can be described by formulae and should run in a usual programming language in the 
computer, it doesn't mean that Bianca and Doris adhere to the same principles. 
Already the rate, with which they manage without technical aids, is a note on the fact that in their
brains probably something runs {\em completely differently \/} to other people. 
How can it otherwise be understood that {\em Mozart \/}, who has heard coincidentally a mass somewhere, could 
write it down later from memory without an error and completely in score? 
Most of all {\em Mozart \/} and {\em Einstein \/} were humans, who had only the luck that they found highest 
social acknowledgment with the results of their unusual networking in the brain. 
Between Rudolf's astute chess strategies and the ability of Mozart to be able to compose a whole opera only 
in his head no gradual difference exists. 
Only the objects are others and the attitude of `normal' humans to them!! 
If Anna says the whole psalter by heart, she belongs in this sense to the degree wavers between genius and 
madness, even if nobody wants to hear her monologues. -- \\ 
In this sanatorium something is rather lugubrious: I can {\em sense\/} it, and Bianca and Doris {\em know\/} 
what it is! 
Perhaps I will finally get to the bottom of it. 
How on earth can Dr.~Weissenborn consider the sisters to be  insane? 
In a surroundings felt hostile by them their encoded communication provides to them a feeling of security. 
Is it different with us so-called `normal' beings in the world outside?
Who is not afraid when using homebanking or with cash dispensers that strangers can access our accounts? 
Nevertheless, nowadays a modern person can no longer manage without secret numbers! 
Madness is a pure definition thing!!'

@@

In spite of thinking hard Martin fails to solve the problem of decoding Bianca's and Doris's secret language. 
Nevertheless he does not give up: He uses a free day to go to Heidelberg and meets {\em Dr.~Praetorius\/} 
from the university Maths Department. 
Martin had got in touch with this man whose name he had traced through the personal catalogue of the university, 

@@

The academic receives him in a friendly way and listens patiently, when Martin tells him about his work, the sisters and 

@@

Then Martin explains to him the encoding technique, as far as he could already analyse it.

@@

the Zivi does not mention this. \\ \\ 

@@

Martin hands him the playing card which he had found behind the bathroom mirror, and the academic 

@@

`I'm sure, you know what prime numbers are?' 

@@

The result, besides, we want to call the {\em auxiliary module\/}.' 

@@

`Can you give me a number which has the following property: 

@@

`Well, one must hit upon this first!', means Martin, `no wonder I have not cracked this problem!' 

@@

The young man gives the academic a disbelieving look. 

@@

But now he is full of confidence that he can communicate with Bianca and Doris in the future without limits. 
Indeed, with the help of the dictaphone, the laptop and his knowledge this should now be possible! 

@@

\begin{center} 
{\bf VII.} 
\end{center} 
Although Martin returns late in the evening to the sanatorium, he still sits down to his laptop and 
maps out a decoding program. 
Already on the bus ride he had made some sketches, describing the decoding concept of Dr.~Praetorius. 
He checks it with the key {\bf 51\,,\,3} for the coding of the sentence I AM BIANCA. 
It runs perfectly. 
Now together with the coding program he already had finished some days ago, Martin disposes of a complete 
interpreter's system for the secret language of the sisters. 
Dr.~Praetorius had forecast correctly that the associated programs are not complicated at all and the 
routines run very quickly. 
One can master separate words or short sentences also with a pocket calculator, but not longer conversations.
Here only the laptop can help. 
Finally, extremely tired, but altogether satisfied with himself, Martin falls into the bed. \\ \\ 
Martin's first task in the morning is to look after `his charges'. 
Rudolf and Anna are late risers, but Bianca and Doris get up very early in the morning. 
Martin nervously enters their room; he has brought the dictaphone and the laptop with him. 
The sisters sit silently at their living room table, they do not react to Martin's friendly `Good morning'. 
They also remain quiet, when he puts both devices on the table.
`This behavior must indicate something!' the Zivi asks himself. `Of course!' it suddenly occours to him.

`The password of the day! At the bathroom mirror!' 
And he's absolutely right, the sisters have hidden deliberately a playing card behind the mirror for him. 
They must have suspected that he will communicate today in their way with them. 
The password of the day reads: 
\begin{center} 
{\bf 681\,,\,151\,\,.}
\end{center} 
Martin turns to the women at the desk. 
He puts in the code key and translates the words GOOD MORNING. 
He reads out the numbers on his display loudly. 
The spell is broken. 
The sisters answer in the code, Martin translates back. 
At first he still uses the dictaphone, but, finally, he notices that it works fine without recording equipment. 
Soon he has the exercise and types the numbers of the women directly during their conversation; his laptop 
translates in lightning speed. 
Certainly, it is a little bit slower than the sisters are accustomed to when talking between themselves because Martin  
needs to use a keyboard. 
But the conversation is fluent, even if rather unusual. \\ 
Gradually Martin passes over from the talk of the insignificance to the doctors and nurses in the house. 
Finally: He types the question with shaky hands in his computer WHAT DO THEY DO WITH YOU IN THE TOWER.
While he is reading out the numbers of the encoding, his throat goes dry. 
It is Doris who answers: 
\begin{center} 
4258, 7182, 9168, 6089, 1734, 9391, 8487, 1363, 853, 10898, 12618, 10512, 172, 7493, 1734, 10229, 7182, 13105 \,\,. 
\end{center} 
`A short answer', thinks Martin, before he operates the key for the execution of the translation. 
It takes less than a second for the machine to work. 
Martin stares aghastly at the screen of his laptop. 
He cannot believe what he is reading. 
But then he acts rapidly. -- \\ \\ 
A few days later a huge scandal is uncovered in the Odenwald clinic and is condemned throughout the nation.

@@

\noindent
{\em Note of the author:\/}
\begin{itemize}
\item[(1)] In order not to confuse the reader, a necessary mathematic
  presupposition was not mentioned with the description of the coding
  procedure.  However it is not required for the purposes of this story.
  Nevertheless, it should be mentioned here on behalf of the completeness
  that not {\em every\/} arbitrary pair of numbers is suitable as a coding
  code where the main module is a product of two prime numbers.  Rather
  the fact that the auxiliary module and the encoding
  exponent have {\em no common devisor\/} should be respected.
  Otherwise no decoding exponent would be found. \\*[+2pt]
  {\bf Example}: The pair 35\,,\,15 is not good as a coding code
  because the auxiliary module \((5-1) \cdot (7-1) =24\) and the coding
  exponent \(15\) have the common divisor \(3\).
\item[(2)] However, in practical applications one does not encode a text literally
as it is described in the story as a so-called RSA-procedure.  One
block-likely codes a text, while one combines the letters of the text
sequentially to blocks of firm length and assigns with a certain procedure
{\em a separate number\/} to these blocks.

\item[(3)] Besides it is usual in the practice -- in contrast to Doris' and
Bianca's method of approach -- to present the coding not in a form of
numerical orders, but in letters which prove naturally nonsense as a text.
